Phenotypic evolution is more constrained in simpler food webs

### 2019-01-09 manuscript.Rmd
edit beginning of discussion to make clear that simpler food webs constrained phenotypic evolution at two levels (trajectory of change and genetic potential).

<!--Summary-->
Our key finding was that phenotypic evolution in gall midges was more constrained in simpler food webs. More traits contributed to the slope of the adaptive landscape in the simpler food web, suggesting that the trajectory of phenotypic evolution is more constrained. Similarly, the simple food-web treatment indirectly increased the number of genetic constraints, which could act to constrain the gall midge's adaptive potential in the face of novel selection pressures. We also found evidence of indirect selection pressures in more complex food webs, suggesting that the adaptive landscape may be more dynamic in complex food webs. Taken together, our study provides experimental evidence from the field that the simplification of ecological communities may constrain the adaptive potential of remaining populations.

>>>>

<!--Summary-->
<!-- Our key finding was that phenotypic evolution in gall midges was more constrained in simpler food webs. More traits contributed to the slope of the adaptive landscape in the simpler food web, suggesting that the trajectory of phenotypic evolution is more constrained. -->
We found that simpler food webs constrained phenotypic evolution in gall midges in two key ways. First, more traits contributed to the slope of the adaptive landscape in the simpler food web, suggesting greater constraints on the trajectory of phenotypic evolution. Second, the simple food-web treatment indirectly increased the number of genetic constraints, which could act to constrain the gall midge's adaptive potential in the face of novel selection pressures. We also found evidence of indirect selection pressures in more complex food webs, suggesting that the adaptive landscape may be more dynamic in complex food webs. Taken together, our study provides experimental evidence from the field that the simplification of ecological communities may constrain the adaptive potential of remaining populations.
